---
title: "data_generation"
output:
  pdf_document: default
  html_document: default
date: "2024-03-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Set up and data generation
## Packages
```{r}
library(dplyr)
library(rdrobust)
library(tidyverse)
```

## Base parameters and variables
We generate data to determine the prices per squared meter in Paris and Issy les Moulineaux. 
```{r}
# Base parameters and variables
n_properties <- 10000
n_years <- 6
N <- n_properties * n_years

# Property IDs repeated across years
PropertyID <- rep(1:n_properties, each = n_years)

# Year variable (repeating for each property)
Year <- rep(1:n_years, n_properties)

# Values > 0 are in Paris, values < 0 are in Issy
# Simulate x and y coordinates
set.seed(123)
X_axis <- runif(n_properties, min = 0, max = 4000)

set.seed(123)
Y_axis <- runif(n_properties, min = -2000, max = 3000)

# Ensure that x and y are repeated across each year for consistency
X_axis <- rep(X_axis, each = n_years)
Y_axis <- rep(Y_axis, each = n_years)

# Determine Region based on y coordinate
Region <- ifelse(Y_axis > 0, "Paris", "Issy")

# Combine all the information into a data frame
data <- data.frame(PropertyID, Year, X_axis, Y_axis, Region)
data <- data %>%
  mutate(Distance_to_Border = Y_axis,
         Treatment = ifelse(Region == "Paris" & Year >= 3, 1, 0))
```

```{r}
# Calculate price
beta0 <- 10000
beta_t <- 350 # Treatment effect
beta1 <- 500 # Shared determinant
beta2 <- -1.7 # Continuous determinant
beta3 <- 200 # Discontinuous determinant
beta4 <- 50 # Local Parallel Trend

data <- data %>%
  mutate(Price_m2 = beta0 + beta_t * Treatment)

head(data)
```

## Common price determinant in Issy and Paris (Balcony in the property)
```{r}
set.seed(123)
balcony_indc <- sample(c(0, 1), size = n_properties, replace = TRUE, prob = c(0.7, 0.3))
balcony_indc <- rep(balcony_indc, each = n_years)
data <- data %>%
  mutate(Balcony_indc = balcony_indc) %>%
  mutate(Price_m2 = beta0 + beta1 * Balcony_indc + beta_t * Treatment)
```


## Border Continuous Determinant in the Price (distance to Eiffel Tower)
We set up the distance to the Eiffel Tower as a Cartesian Distance assuming the Eiffel Tower to be at the coordinates (0;3400).
```{r}
data <- data %>%
  mutate(Distance_to_EiffelTower = sqrt(X_axis^2 + (Y_axis - 3400)^2),
         Price_m2 = beta0 + beta1 * Balcony_indc + beta2 * Distance_to_EiffelTower + beta_t * Treatment)
```

## Discontinuous Determinant in the Price (access to the metro)
```{r}
data <- data %>%
  mutate(Metro_access = ifelse(Region == "Paris", 1, 0),
         Price_m2 = beta0 + beta1 * Balcony_indc + beta2 * Distance_to_EiffelTower + beta3 * Metro_access + beta_t * Treatment)
```

## Price Determinant following a Local Parallel Trend (real estate speculation)
```{r}
# Price Determinant following a Local Parallel Trend (real estate speculation)
border_range <- 500
initial_local_trend_value <- 100
local_growth_rate <- 0.04  # Assuming a 4% annual local trend growth

data <- data %>%
  mutate(Local_Trend = ifelse(abs(Distance_to_Border) <= border_range & Year == 1, initial_local_trend_value, 200))

for (year in 2:n_years) {
  data <- data %>%
    group_by(PropertyID) %>%
    mutate(Local_Trend = ifelse(Year == year & abs(Distance_to_Border) <= border_range, lag(Local_Trend) * (1 + local_growth_rate), Local_Trend)) %>%
    ungroup()
}

for (year in 2:n_years) {
  data <- data %>%
    group_by(PropertyID) %>%
    mutate(Local_Trend = ifelse(Year == year & Distance_to_Border > border_range, lag(Local_Trend) * (1 + 0.08), Local_Trend)) %>%
    ungroup()
}

for (year in 2:n_years) {
  data <- data %>%
    group_by(PropertyID) %>%
    mutate(Local_Trend = ifelse(Year == year & Distance_to_Border < - border_range, lag(Local_Trend) * (1 + 0.06), Local_Trend)) %>%
    ungroup()
}

data <- data %>%
  mutate(Price_m2 = beta0 + beta1 * Balcony_indc + beta2 * Distance_to_EiffelTower + beta3 * Metro_access + beta4 * Local_Trend + beta_t * Treatment)
```

## Noise
```{r}
# Disrupt the Grembi regression => double the noise in the post-treatment period
noise_level <- 50
data$asymmetric_noise <- ifelse(data$Year > 3, rnorm(N, 0, noise_level*2), rnorm(N, 0, noise_level))

# Update prices
data <- data %>%
  mutate(Price_m2 = beta0 + beta1 * Balcony_indc + beta2 * Distance_to_EiffelTower + beta3 * Metro_access + beta4 * Local_Trend + beta_t * Treatment + asymmetric_noise)

```

```{r}
write.csv(data, "~/Desktop/Diff-in-Disc/Simulation/sim_data.csv")
```
