---
title: "Eval_methods"
output:
  pdata_document: default
  html_document: default
date: "2024-03-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Package Installation
```{r}
library(dplyr)
library(rdrobust)
library(knitr)
library(kableExtra)
library(ggplot2)
```

```{r}
# Load data from the simulated database
data <- read.csv('~/Desktop/Diff-in-Disc/Simulation/sim_data.csv')
df <- data
```
# Treatment estimation methods
## Diff-in-diff
We set up treatment group and treatment period indicators and an interaction term to do a DiD regression
```{r}
# Create a dummy variable to indicate the time when the treatment started
data <- data %>%
  mutate(time_indc = ifelse(Year >= 3, 1, 0),
         treated_indc = ifelse(Region == 'Paris', 1, 0),
         did = time_indc * treated_indc)

# DiD Regression 
didreg <- lm(Price_m2 ~ treated_indc + time_indc + did, data = data)
summary(didreg)

coef_did <- didreg$coefficients[[4]]
```

## Regression Discontinuity
```{r}
rdd <- rdrobust(y = data$Price_m2,
                x = data$Distance_to_Border, 
                all = T,
                subset = data$Year == 3,
                )
summary(rdd)
coef_rdd <- rdd$Estimate[[2]]
```

## Biased Diff-in-Disc
```{r}
# Diff-in-Disc over the entire sample
grembi_equation <- Price_m2 ~ Distance_to_Border + treated_indc*(1+Distance_to_Border)+time_indc*(1+Distance_to_Border) +did*(1+Distance_to_Border)

# Run regression
biased_grembi <- lm(formula = grembi_equation, data = data)
coef_grembi_no_bw <- biased_grembi$coefficients[[4]]
summary(biased_grembi)
```

## Biased Results summary
```{r}
# Save in vectors
Biased_coefs <- c(coef_did, coef_rdd, coef_grembi_no_bw)
Bias_vec <- c(coef_did-350, coef_rdd-350, coef_grembi_no_bw-350)

biased_methods <- data.frame(
  Coefficient = Biased_coefs,
  Bias = Bias_vec)

rownames(biased_methods) <- c("Diff-in-Diff", "RDD", "Full-sample Regression")

# Presentations table
kable(biased_methods, caption = "Estimation of the Treatment effect with different methods") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, 
                position = "center")
```


```{r}
ggplot(data %>% filter(Year==3)) + 
  aes(y=Price_m2, x=Distance_to_Border) + 
  geom_point()
```

# Diff-in-Disc

## AVG BW
### Triangular Kernel
```{r}
# Get BW for pre and post-treatment
rdd_before_tri <- rdrobust(y = data$Price_m2, x = data$Distance_to_Border, all = T,
                subset = data$Year<3, kernel = "tri")
rdd_after_tri <- rdrobust(y = data$Price_m2, x = data$Distance_to_Border, all = T,
                subset = data$Year >=3, kernel = "tri")

# Construct BW by averaging both bandwidths
left_bw_tri <- rdd_before_tri$bws[1]
right_bw_tri <- rdd_after_tri$bws[1]
optimal_bw_avg_tri <- (left_bw_tri+right_bw_tri)/2

# Perform the regression
w_tri_avg <- rdd_k_weights(x=data$Distance_to_Border, c=0, h=optimal_bw_avg_tri, 
                           kernel = "triangular")

grembi_model_tri <- lm(formula = grembi_equation, data = data,
                       subset = abs(Distance_to_Border) < optimal_bw_avg_tri,
                       weights = w_tri_avg)

avg_bw_coef_tri <- grembi_model_tri$coefficients[[5]] # save coef
```

### Uniform Kernel
```{r}
# Repeat the procedure
rdd_before_uni <- rdrobust(y = data$Price_m2, x = data$Distance_to_Border, all = T,
                subset = data$Year<3, kernel = "uni")

rdd_after_uni <- rdrobust(y = data$Price_m2, x = data$Distance_to_Border, all = T,
                subset = data$Year >=3, kernel = "uni")

# Same for the BW
left_bw_uni <- rdd_before_uni$bws[1]
right_bw_uni <- rdd_after_uni$bws[1]
optimal_bw_avg_uni <- (left_bw_uni+right_bw_uni)/2

# Same for regression
w_uni_avg <- rdd_k_weights(x=data$Distance_to_Border, c=0, h=optimal_bw_avg_uni, 
                           kernel = "uniform")

grembi_model_uni <- lm(formula = grembi_equation, data = data,
                       subset = abs(Distance_to_Border) < optimal_bw_avg_uni,
                       weights = w_uni_avg)

avg_bw_coef_uni <- grembi_model_uni$coefficients[[5]] # save coef
```

## Imbens Plug-in Bandwidth
### Triangular Kernel
```{r}
# Get bandwidth
h_imbens_tri <- Imbens_BW(y=data$Price_m2, x=data$Distance_to_Border,
                       c=0, kernel = "triangular")
# Get weights
w_tri_imbens <- rdd_k_weights(x=data$Distance_to_Border, c=0, h=h_imbens_tri)

# Run the regression
tri_imbens <- lm(formula = grembi_equation, data = data,
                 subset = abs(Distance_to_Border) < h_imbens_tri, 
                 weights = w_tri_imbens)
imbens_coef_tri <- tri_imbens$coefficients[[5]] # save coef
```

### Uniform kernel 
```{r}
# Idem
h_imbens_uni <- Imbens_BW(y=data$Price_m2, x=data$Distance_to_Border,
                       c=0, kernel = "uniform")

w_uni_imbens <- rdd_k_weights(x=data$Distance_to_Border, c=0, h=h_imbens_uni, 
                              kernel = "uniform")

uni_imbens <- lm(formula = grembi_equation, data = data,
                 subset = abs(Distance_to_Border) < h_imbens_uni, 
                 weights = w_uni_imbens)

imbens_coef_uni <- uni_imbens$coefficients[[5]] # save coef

```

## Adaptive SGD
### Triangular kernel
```{r}
# Same steps as before
BW_T <- DiRD_BW(y=data$Price_m2, x=data$Distance_to_Border, c=0, t0=3,
                time_var = data$Year, ID=data$PropertyID)$optimal_h[1]

# Weights
w_tri_sgd <- rdd_k_weights(x=data$Distance_to_Border, c=0, h=BW_T, kernel = "triangular")

# Regression and coef
reg_tri_sgd <- lm(formula = grembi_equation, data = data, 
                  subset = abs(Distance_to_Border) < BW_T, weights = w_tri_sgd)
reg_tri_sgd_coef <- reg_tri_sgd$coefficients[[5]]
```

### Uniform kernel 
```{r}
# Idem
BW_U <- DiRD_BW(y=data$Price_m2, x=data$Distance_to_Border, c=0, t0=3,
                time_var = data$Year, ID=data$PropertyID, kernel = "uniform")$optimal_h[1]

w_uni_sgd <- rdd_k_weights(x=data$Distance_to_Border, c=0, h=BW_U, kernel = "uniform")

unif_sgd <- lm(formula = grembi_equation, data = data, 
               subset = abs(Distance_to_Border) < BW_U,
               weights = w_uni_sgd)

unif_sgd_coef <- unif_sgd$coefficients[[5]]
```

# Results summary
```{r}
# Create the data frame
bw_and_coef_table <- data.frame(
  Kernel = c("Triangular", "Uniform", "Triangular", "Uniform", "Triangular", "Uniform"),
  `Imbens Plug-in Bandwidth Estimator` = c(h_imbens_tri, h_imbens_uni, NA, NA, NA, NA),
  `AVG of 2 bandwidths` = c(NA, NA, optimal_bw_avg_tri, optimal_bw_avg_uni, NA, NA),
  `Adaptive SGD` = c(NA, NA, NA, NA, BW_T, BW_U),
  `Treatment Effect` = c(imbens_coef_tri, imbens_coef_uni, avg_bw_coef_tri, avg_bw_coef_uni, reg_tri_sgd_coef,
                         unif_sgd_coef)
)

# Print the table
kable(bw_and_coef_table,
      col.names = c("Kernel", "Imbens Plug-in Bandwidth Estimator", 
                    "AVG of 2 bandwidths", "Adaptive SGD", "Treatment Effect"))

```

