---
title: "DiRD_BW-log-MSE"
output:
  pdf_document: default
  html_document: default
date: "2024-04-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Ce document recapitule l'ensemble de fonctions utilisées pour trouver la bandwidth optimale pour estimation d'un effet de traitement avec la méthode de Difference-in-Regression-Discontinuity (DiRD) ou Diff-in-Disc.

```{r}
library(ggplot2)
# Read data
df <- read.csv(here::here("Simulation/sim_data.csv"))
```

# Prior Functions
## log_MSE_DiRD
Cette fonction nous permet de calculer la MSE d'une régression linéaire adaptée a un contexte de Diff-in-Disc. Cette équation d'estimation correspond à celle qui a été présentée dans l'article de V. Grembi 'Do Fiscal Rules Matter?' (2016) :
$$ y_{it} = \beta_0+\beta_1X_i+ 1_{\{X\geq c\}}(\alpha_0+\alpha_1X_i)+1_{\{t\geq t_0\}}(\gamma_0+\gamma_1X_i)+
1_{\{X\geq c\}}1_{\{t\geq t_0\}}(\tau+\lambda_0X_i)+\varepsilon_{it} $$
Où $\tau$ est l'effet du traitement.

```{r}
log_MSE_DiRD <- function(y, x, time_var, c, t0){
  # Prepare regression
  reg_data <- data.frame(y, x, time_var)
  
  # Treatment start indicator
  reg_data$time_indc <- ifelse(reg_data$time_var >= t0, 1, 0)
  
  # Treatment group indicator
  reg_data$group_indc <- ifelse(reg_data$x >= c, 1, 0)
  
  # Interaction between time and treated
  reg_data$dird <- reg_data$time_indc * reg_data$group_indc
  
  # Check if the data is valid for regression
  if (nrow(reg_data) == 0 || sum(!is.na(reg_data$y)) == 0) {
    print("Insufficient data")
  }
    else{
      # Regression model
      model<- lm(y ~ x + group_indc*(1+x) + time_indc*(1+x) + dird*(1+x), data=reg_data)
      log_mse <- log(mean(resid(model)^2)+1)
    }
  return(log_mse)
  }
```

## find_next_h
In this context, we "manually" compute the gradient of the MSE function to perform a stochastic gradient descent by randomly selecting a bandwidth value $(h_0)$ and then finding the value for h just above it to compute this "infinitesimal calculation".
```{r}
# Function to find the closest h given a current h value from a BW set
find_next_h <- function(current_h, h_values) {
  # Ensure h_values is not empty
  if (length(h_values) == 0) {
    stop("h_values cannot be empty")
  }
  # Subset to find all values greater than the current h
  possible_values <- h_values[h_values > current_h]
  
  # If there are any higher values, return the minimum
  if (length(possible_values) > 0) {
    return(min(possible_values))
  } else {
    
    # Find values less than the current h and return the maximum of these
    lower_values <- h_values[h_values < current_h]
    if (length(lower_values) > 0) {
      return(max(lower_values))
      
    } else {
      # No higher or lower values available = stop
      stop("No higher or lower values found for the given h")
    }
  }
}
```

# Main Functions
## MSE_Gradient_0 
This function is used to calculate the Gradient of the MSE corresponding to the randomly chosen $h_0$. 
This will later be used as our initalisation for the Stochastic Gradient Descent Algorithm for MSE minimization.This function uses both of the previous functions.\\
MSE_Gradient0 function yields a vector with 2 parameters for results : a random BW (h_0) and its respective MSE Gradient (Gradient_0).
```{r}
log_MSE_Gradient0 <- function(y, x, h, data, ID, c, time_var, t0){
  # get a df with all unique IDs
  data_unique <- data[!duplicated(data$ID),]
  unique_h_values <- data_unique$h
  
  # Randomly pick a random h and the one just above (h_plus)
  random_index <- sample(1:nrow(data_unique), 1)
  h_0 <- data_unique$h[random_index] # rnd h
  h_plus <- find_next_h(current_h = h_0, h_values = unique_h_values) # h just above
  
  # Subset by |x| < h and compute MSE (for h_0)
  eval_sample <- subset(data, subset = h < h_0)
  # Repeat the process for h_plus
  sample_plus <- subset(data, subset = h < h_plus)
  
  
  if (nrow(eval_sample) == 0 || nrow(sample_plus) == 0) {
    # Handle empty data scenario
    # If data is insufficient, re-run the function
    return(log_MSE_Gradient0(y, x, h, data, ID, c, time_var, t0))  # Skip to the next iteration
  } else {
    # Calculate MSEs for bothsubsets
    log_mse_0 <- log_MSE_DiRD(y = eval_sample$y, x=eval_sample$x, 
                      time_var = eval_sample$time_var, c=c, t0 = t0)
    log_mse_plus <- log_MSE_DiRD(y = sample_plus$y, x=sample_plus$x, 
                         time_var = sample_plus$time_var, c=c, t0 = t0)
  }
  # Gradient
  log_MSE_gradient <-  (log_mse_0-log_mse_plus)/max((h_0-h_plus), 1e-08)
  return(c(h_0, log_MSE_gradient))
}
```

## DiRD_BW 

This function recompiles every function created so far to perform a Stochastic Gradient Descent to minimize the MSE of our regression to find the optimal bandwidth. \\
This function is basically divided in 2 loops : \\
The 'while' loop uses a gradient descent algorithm with an ADAGrad method for computing and updating the learning rate.\\ 
The 'for' loop acts as the "stochastic part" in SGD to compare local minima to find a global minimum.\\


```{r}
DiRD_BW_log <- function(y, x, c, time_var, t0, ID, max_iter=100, max_epochs=500){
  ## Initialisation
  
  # Preparation
  # Set up h as the 'bandwidth variable'
  data <- data.frame(ID=ID, y=y, x=x, time_var=time_var)
  data$h <- abs(data$x)
  
  # Initialize parameters : 'for' loop
  h_vector <- c()
  log_mse_vector <- c()
  initial_lr <- 0.01
  epsilon <- 1e-8
  
  for(i in 1:max_epochs){
    
    # Initialisation : h0 and gradient0 to do a stochastic gradient descent
    gradient_details <- log_MSE_Gradient0(y=y, x=x, h=data$h, data=data, ID=ID, c=c, time_var=time_var, t0=t0)
    h_0 <- gradient_details[1]
    log_Gradient_0 <- gradient_details[2]
    h_j <- h_0
    log_Gradient_j <- log_Gradient_0
    accumulated_sq_grad <- log_Gradient_j^2
    
    # Prep iterations
    iter_count <- 0
    
    # MSE convergence criterion
    all_gradients <- c()
    
    # Inside your while loop, after calculating Gradient_j, add it to all_gradients
    all_gradients <- c(all_gradients, abs(log_Gradient_j))
    edf <- ecdf(all_gradients)
    
    # Calculate dynamic threshold presented by Gilli, 2006
    if (length(all_gradients) > 1) {
      dynamic_threshold <- quantile(edf, 0.8 * max_epochs - i / max_epochs) # As per TA algorithm (Gilli & al.)
    } else {
      dynamic_threshold <- 2  # Default threshold for the first epoch
    }
    while(abs(log_Gradient_j) > dynamic_threshold){
      iter_count <- iter_count + 1

      # AdaGrad update for log_Gradient_j
      accumulated_sq_grad <- accumulated_sq_grad + log_Gradient_j^2
      if (accumulated_sq_grad + epsilon > 0) {  # Check to avoid NaNs from sqrt
        adjusted_lr <- initial_lr / sqrt(accumulated_sq_grad + epsilon)
      } else {
        adjusted_lr <- initial_lr  # Fallback if denominator is zero
      }      
      h_j <- abs(h_j - adjusted_lr * log_Gradient_j)  # Apply update
      
      # Sort data by unique h values to find the closest h value (h_j_plus)
      unique_h_values <- sort(unique(data$h))
      h_j_plus <- find_next_h(h_j, unique_h_values)
      
      if (h_j_plus < h_j){
        break
      }
      
      # Break when you get to the max_iterations
      if (iter_count >= max_iter){
        break
      }
      
      # Subset by |x| < h and compute MSE 
      sample_j <- subset(data, subset = abs(x) < h_j)
      sample_j_plus <- subset(data, subset = abs(x) < h_j_plus)
      
      if (nrow(sample_j) == 0 || nrow(sample_j_plus) == 0) {
        # Handle empty data scenario
        next  # Skip to the next iteration
      } else {
        # Calculate MSEs for bothsubsets
        log_mse_j <- log_MSE_DiRD(y = sample_j$y, x=sample_j$x, 
                          time_var = sample_j$time_var, c=c, t0 = t0)
        log_mse_j_plus <- log_MSE_DiRD(y = sample_j_plus$y, x=sample_j_plus$x, 
                               time_var = sample_j_plus$time_var, c=c, t0 = t0)
      }
      
      # Compute Gradient
      log_Gradient_j <- (log_mse_j - log_mse_j_plus) / max((h_j - h_j_plus), 1e-05)
    }
    
    # h_j is the local minimizer for MSE
    h_vector <- c(h_vector, h_j)
    log_mse_vector <- c(log_mse_vector, log_mse_j)  # Log-transform MSE to stabilize variance
  }

  local_minima <- data.frame(h=h_vector, log_mse=log_mse_vector)
  # Find the h corresponding to the minimal mse
  minimal_mse_h <- local_minima$h[which.min(local_minima$log_mse)]
  
  mse_plot <- ggplot(local_minima, aes(x = h, y = log_mse)) +
    geom_line() +
    geom_point() +
    labs(title = "Evolution of log-MSE over h values", x = "Bandwidth (h)", y = "MSE") +
    theme_minimal()
  
  return(list( optimal_h = minimal_mse_h, 
              min(local_minima$log_mse),
              plot = mse_plot))
}
```

Finally we have the results given by the 'DiRD_BW' function
```{r}
DiffinDisc_BW_log <- DiRD_BW_log(y=df$Price_m2, x=df$Distance_to_Border, c=0, time_var=df$Year, t0=3,
        ID=df$PropertyID)

DiffinDisc_BW_log
```
