---
title: "BW_Functions"
output:
  pdf_document: default
  html_document: default
date: "2024-04-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# The code lives in BW_Functions.R; each chunk below displays one labelled section of it
knitr::read_chunk("BW_Functions.R")
```

Ce document recapitule l'ensemble de fonctions utilisées pour trouver la bandwidth optimale pour estimation d'un effet de traitement avec la méthode de Difference-in-Regression-Discontinuity (DiRD) ou Diff-in-Disc.

# Imbens Plug-in Bandwidth Function
```{r Imbens_BW}
```


# Prior Functions

## rdd_k_weights
Calculates kernel weights for observations in a data set given a specific kernel type. These weights are used in regression discontinuity design (RDD) analyses. Very similar function to Cattaneo's rdrobust "rdrobust_kweight" function.

```{r rdd_k_weights}
```

## MSE_DiRD
Cette fonction nous permet de calculer la MSE d'une régression linéaire adaptée a un contexte de Diff-in-Disc. Cette équation d'estimation correspond à celle qui a été présentée dans l'article de V. Grembi 'Do Fiscal Rules Matter?' (2016) :
$$ y_{it} = \beta_0+\beta_1X_i+ 1_{\{X\geq c\}}(\alpha_0+\alpha_1X_i)+1_{\{t\geq t_0\}}(\gamma_0+\gamma_1X_i)+
1_{\{X\geq c\}}1_{\{t\geq t_0\}}(\tau+\lambda_0X_i)+\varepsilon_{it} $$
Où $\tau$ est l'effet du traitement.

La fonction renvoie `NA` si l'une des quatre cellules (groupe x période) a moins de 3 observations : avec 8 paramètres, la régression s'ajusterait parfaitement et la MSE serait artificiellement proche de 0.

```{r MSE_DiRD}
```


```{r MSE_penalty}
```

## penalized_MSE
Objective function of the algorithm, $J(h) = p(h) \cdot MSE(h)$, computed on every observation such that $|X_i - c| < h$. `N` is the size of the full sample.
```{r penalized_MSE}
```


## find_next_h
In this context, we "manually" compute the gradient of the MSE function to perform a stochastic gradient descent by randomly selecting a bandwidth value $(h_0)$ and then finding the value for h just above it to compute this "infinitesimal calculation".
```{r find_next_h}
```

# Main Functions
## MSE_Gradient_0 
This function is used to calculate the Gradient of the MSE corresponding to the randomly chosen $h_0$. 
This will later be used as our initialization for the Stochastic Gradient Descent Algorithm for MSE minimization.This function uses both of the previous functions.\\
MSE_Gradient0 function yields a vector with 3 values: a random BW (h_0), the next BW (h_plus) and the MSE Gradient at h_0 (Gradient_0). It returns `NA`s if no computable h_0 is found after 100 draws.

`h_candidates` are the values h_0 can be drawn from (the current quantile interval), while `h_values` are all the bandwidths of the sample. The MSE is always computed on the full `data` with $|X_i - c| < h$.
```{r MSE_Gradient0}
```

## DiRD_BW 

This function compiles every function created so far to perform a Stochastic Gradient Descent to minimize the MSE of our regression to find the optimal bandwidth. \\
This function is basically divided in 2 loops : \\
We will call the while loop a for loop that ahs several stopping criteria. The 'while' loop uses a gradient descent algorithm with an ADAGrad method for computing and updating the learning rate.\\ 
The 'for' loop acts as the "stochastic part" in SGD to compare local minima to find a global minimum.\\


```{r DiRD_BW}
```

