---
title: "Monte Carlo comparison of Diff-in-Disc bandwidth selectors"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 9, fig.height = 5.5, dpi = 150)
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(kableExtra)

mc <- readRDS(here::here("Simulation/MonteCarlo/results/mc_results.rds"))
tau_true <- mc$tau
res <- mc$results %>%
  mutate(covered = ci_low <= tau_true & tau_true <= ci_high,
         design = factor(design, c("sharp", "smooth")),
         kernel = factor(kernel, c("triangular", "uniform")))
selectors <- c("IK plug-in", "AVG rdrobust", "SGD criterion", "FD rdrobust")

# Chart chrome (reference palette, light surface)
ink <- "#0b0b0b"; ink_2 <- "#52514e"; muted <- "#898781"; grid_col <- "#e1e0d9"
kernel_cols <- c(triangular = "#2a78d6", uniform = "#eb6834")
theme_mc <- theme_minimal(base_size = 12) +
  theme(text = element_text(colour = ink), axis.text = element_text(colour = ink_2),
        panel.grid.major = element_line(colour = grid_col, linewidth = 0.3),
        panel.grid.minor = element_blank(), strip.text = element_text(face = "bold"),
        plot.background = element_rect(fill = "#fcfcfb", colour = NA),
        legend.position = "top")
```

## Set-up

`r mc$R` replications of the Paris / Issy-les-Moulineaux panel (10,000 properties, 6 years, true effect $\tau = `r tau_true`$), generated by `dgp.R` under two designs that share the random draws (replication $r$ uses seed $10000 + r$):

- **sharp**: the thesis design. The local trend is identical on both sides of the border within 500 m and jumps beyond it, so any bandwidth up to 500 m is unbiased.
- **smooth**: the same trends, but the gap between both sides grows gradually with the distance to the border. The local linear fit is biased for any $h > 0$, and the bias grows with $h$ (the usual bias-variance trade-off).

Unlike `data_generation.Rmd`, the coordinates and the balcony are drawn independently (see `dgp.R`).

Every selector feeds the same local linear Diff-in-Disc regression (Grembi et al., 2016), except FD rdrobust:

| Selector | Bandwidth | Estimate and CI |
|---|---|---|
| IK plug-in | Imbens & Kalyanaraman (2012) on the pooled sample | Grembi regression, 95% CI with SE clustered by property |
| AVG rdrobust | mean of the rdrobust bandwidths before and after $t_0$ (Grembi et al.) | same |
| SGD criterion | minimizer of the adaptive SGD objective $J(h)$ | same |
| FD rdrobust | rdrobust on the property-level change in price | rdrobust estimate, robust bias-corrected 95% CI |

## Results

```{r summary-table}
summary_tab <- res %>%
  filter(method %in% selectors) %>%
  group_by(design, kernel, method) %>%
  summarise(`Median h` = median(h), Bias = mean(tau) - tau_true, SD = sd(tau),
            RMSE = sqrt(mean((tau - tau_true)^2)), `Mean SE` = mean(se),
            Coverage = mean(covered), .groups = "drop") %>%
  mutate(method = factor(method, selectors)) %>%
  arrange(design, kernel, method)

summary_tab %>%
  mutate(Coverage = sprintf("%.1f%%", 100 * Coverage)) %>%
  select(-design) %>%
  kable(digits = 1, col.names = c("Kernel", "Selector", "Median h", "Bias", "SD", "RMSE",
                                  "Mean SE", "95% CI coverage"),
        caption = "Performance of each selector (true effect = 350)") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) %>%
  pack_rows(index = table(summary_tab$design))
```

```{r tau-distribution, fig.height = 6}
# The view is limited to x_range; the share of estimates outside it is printed on the right
x_range <- c(250, 450)
dist <- res %>%
  filter(method %in% selectors) %>%
  mutate(method = factor(method, rev(selectors)))
outside <- dist %>%
  group_by(design, kernel, method) %>%
  summarise(share = mean(tau < x_range[1] | tau > x_range[2]), .groups = "drop") %>%
  filter(share > 0) %>%
  mutate(label = sprintf(ifelse(share < 0.01, "%.1f%% outside", "%.0f%% outside"), 100 * share))

ggplot(dist, aes(x = tau, y = method)) +
  geom_vline(xintercept = tau_true, colour = muted, linetype = "dashed", linewidth = 0.4) +
  geom_boxplot(fill = "#cde2fb", colour = "#2a78d6", linewidth = 0.4, width = 0.55,
               outlier.size = 0.6, outlier.alpha = 0.4) +
  geom_text(data = outside, aes(x = x_range[2], label = label), hjust = 1, nudge_y = 0.42,
            size = 3, colour = ink_2) +
  coord_cartesian(xlim = x_range) +
  facet_grid(kernel ~ design, labeller = label_both) +
  labs(x = expression(hat(tau) ~ "(dashed line: true effect)"), y = NULL,
       title = "Distribution of the estimated effect across replications") +
  theme_mc
```

```{r takeaway-values}
val <- function(dsg, k, m, col) {
  summary_tab[[col]][summary_tab$design == dsg & summary_tab$kernel == k & summary_tab$method == m]
}
sgd <- res %>% filter(method == "SGD criterion")
share_edge <- mean(abs(sgd$h[sgd$design == "sharp"] - 500) < 20)
others_sharp_tri <- summary_tab %>% filter(design == "sharp", kernel == "triangular",
                                           method != "SGD criterion")
```

**Takeaways**

- **sharp design.** The SGD criterion lands within 20 m of the 500 m edge of the unbiased zone in `r sprintf("%.1f%%", 100 * share_edge)` of the replications, and has the lowest RMSE: with the triangular kernel `r sprintf("%.1f", val("sharp", "triangular", "SGD criterion", "RMSE"))`, against `r sprintf("%.1f", min(others_sharp_tri$RMSE))` to `r sprintf("%.1f", max(others_sharp_tri$RMSE))` for the other selectors. With the uniform kernel, a few replications jump to a distant local minimum of $J(h)$, which inflates its RMSE.
- **smooth design.** The SGD criterion picks bandwidths far above the oracle, and its CI coverage collapses (`r sprintf("%.1f%%", 100 * val("smooth", "triangular", "SGD criterion", "Coverage"))` with the triangular kernel). $J(h)$ is a penalized residual MSE, not the MSE of $\hat\tau$: the penalty rewards larger samples, and nothing in $J$ accounts for a bias that grows smoothly with $h$. It detects a sharp break in the data, but it does not trade bias off against variance.
- **FD rdrobust** stays close to the oracle RMSE with nominal coverage in both designs. **AVG rdrobust**, the approach of Grembi et al., under-covers in the smooth design (`r sprintf("%.1f%%", 100 * val("smooth", "triangular", "AVG rdrobust", "Coverage"))` triangular, `r sprintf("%.1f%%", 100 * val("smooth", "uniform", "AVG rdrobust", "Coverage"))` uniform).

## Where is the best bandwidth?

Each replication is also estimated at fixed bandwidths, which gives the RMSE of the Grembi regression as a function of $h$. Its minimum is the infeasible **oracle** bandwidth that a selector would ideally find.

```{r rmse-curve}
fixed <- res %>%
  filter(method == "Fixed h") %>%
  group_by(design, kernel, h) %>%
  summarise(RMSE = sqrt(mean((tau - tau_true)^2)), .groups = "drop")
oracle <- fixed %>% group_by(design, kernel) %>% slice_min(RMSE, n = 1) %>% ungroup()
chosen <- res %>%
  filter(method %in% selectors, method != "FD rdrobust") %>%
  group_by(design, kernel, method) %>%
  summarise(h = median(h), .groups = "drop")

ggplot(fixed, aes(x = h, y = RMSE, colour = kernel, linetype = kernel)) +
  geom_line(linewidth = 0.7) +
  geom_point(size = 2.2) +
  geom_point(data = oracle, shape = 21, size = 4.5, stroke = 1, fill = NA,
             show.legend = FALSE) +
  facet_wrap(~ design, labeller = label_both) +
  scale_colour_manual(values = kernel_cols) +
  scale_x_continuous(breaks = c(100, 200, 300, 400, 500, 600, 800, 1000)) +
  scale_y_log10() +
  labs(x = "Bandwidth h (m)", y = "RMSE of the estimated effect (log scale)",
       colour = "Kernel", linetype = "Kernel",
       title = "RMSE of the local linear Diff-in-Disc by bandwidth",
       subtitle = "Rings mark the oracle bandwidth (lowest RMSE) of each kernel") +
  theme_mc
```

```{r chosen-table}
chosen %>%
  pivot_wider(names_from = method, values_from = h) %>%
  left_join(oracle %>% select(design, kernel, `Oracle h` = h), by = c("design", "kernel")) %>%
  kable(digits = 0, caption = "Median bandwidth chosen by each selector vs the oracle") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE)
```

## Does DiRD_BW find the minimum of its own objective?

The Monte Carlo minimizes $J(h)$ with a grid refined by golden-section search, which is much faster than running `DiRD_BW` in every replication. Both were run on the first `r max(mc$sgd_check$rep)` replications of each design:

```{r sgd-check}
mc$sgd_check %>%
  mutate(`h diff (m)` = h_sgd - h_grid, `J diff (%)` = 100 * (J_sgd - J_grid) / J_grid) %>%
  group_by(design, kernel) %>%
  summarise(`Max |h diff| (m)` = max(abs(`h diff (m)`)),
            `Max |J diff| (%)` = max(abs(`J diff (%)`)), .groups = "drop") %>%
  kable(digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE)
```
